Crowdy: Social Crowd Visualization

### 2011-03-29 docs/crowdy_gui.tex
added crowd view to docs

We apply the Simile Timeline library which is developed by MIT's Computer Science
and Artificial Intelligence Laboratory. BLAHBLAH WAITING JEFF'S STUFF.

The timeline view

@@

>>>>

We apply the Simile Timeline library which is developed by MIT's Computer
Science and Artificial Intelligence Laboratory. The timeline shows all of the
crowds at a given time span.  The timeline allows the analyist to zoom in on a
specific time, and move forward and backward thorough time.  The visualization
shows how long the crowd lasts, and the size of the crowd. We may make the
crowd taller or shorter based on the size of the crowd.  We will also display a
few keywords from each crowd.

@@

\subsubsection{Crowd View}
When an analyst clicks a crowd in the list, timeline, or map view, we show an
expanded view of the crowd. This is a form of progressive disclosure, where we
give the analyst more information as they need it.  At the moment, we just show
a network graph where nodes represent users, and edges represent the tweets
between users. We plan to add the ability to drill down even more.  When the
analyst clicks on a node, we can give the analyst more information about the
user that was clicked on. When the analyst clicks on an edge, we can show the
conversation between two users.
